---
title: "Untitled"
author: "Simon Ress"
date: "09.09.2021"

#Enable two column-option on slides
classoption: 
- twocolumn
#Output options and formatting
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#Create .md-file from .rmd-files (needs to be saved in same folder [!!not subfolder!!], because of paths)
  #library(rmarkdown)
  #render("test.Rmd", output_file = "test_md.md", md_document(preserve_yaml = TRUE))
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Two columns

Here is some text above



:::::::::::::: {.columns}
::: {.column width="40%"}

contents 1...

:::
::: {.column width="60%"}

contents 2...

:::
::::::::::::::



and here some text below
